Program Transformations for miniKanren

### 2020-07-03 papers/aplas/evaluation.tex
Evaluation in progress.

We focused on these particular examples because they are examples of relational interpreters which are natural and observable.

>>>>

We focused on these particular examples because they are examples of relational interpreters which are natural and observable.
In this study we only measured the execution time for sample queries.
The measured time was averaged over multiple runs for every query.
The queries were run on a laptop running Ubuntu 18.04 with quad core Intel Core i5 2.30GHz CPU and 8 GB of RAM.

\todo{intro sentence.}
Row Original contains the execution time of the original version of the program before any transformations.
Row Ecce corresponds to the result of the transformation with Ecce conjunctive partial deduction system.
Row Non-CPD --- translation by our implementation of nonconjunctive partial deduction.
Etalon --- the etalon implementation of the same program.
CPD --- the earlier implementation of the conjunctive partial deduction for \mk{}.
Brancing --- the earlier implemenctation of CPD for \mk{} with the branching heuristic.
